Biogears in Anesthesia Screen Based Simulation

### 2016-02-17 paper_working_on/paper.tex
add bleeding out scenario intro

Inspired by the previous work from this paper \cite{measure_repeatability}

>>>>

Inspired by the previous work from this paper \cite{measure_repeatability}, we think the quality of a simulation system will also be determined by the stability of experiments under the same or similar circumstances. After consulting with physicians from UPMC and Biogears team, we enumerate several representative experiments and ran both Biogears and CAE simulation on them. Later we presented the result in graphs and tables for visuality.

\subsection{Bleeding Out Scenarios}

Bleeding patients are often seen in trauma and emergency rooms. The cause of this symptom varies. Car accident, Blood vessel abnormalities, blood disorders, tumors, to name a few. We believe that to see how simulation engine reacts to a patient who is suffering from bleeding would be a good way to see how it models human bodies change as time goes by.

To run this experiment on Biogears, we tested it using built-in GUI of Biogears that provides dozens of substances simulation.
